Model Order Selection and Eigen Similarity based Framework for Detection and Identification of Network Attacks

### 2019-05-17 docs/papers/2016JNCA/2016JNCA.tex
compiling version with all chapters
changing what?

\journal{ Journal of Network and Computer Applications}

@@

In this paper, scalars are denoted by italic letters (\emph{a, b, A, B, $α$, $β$}), vectors by lowercase bold letters (\textbf{a, b}), matrices by uppercase bold letters (\textbf{A, B}), and $a_i,_j$ denotes the (\emph{i, j}) elements of the matrix \textbf{A}. The superscripts \textsuperscript{T} and \textsuperscript{-1} are used for matrix transposition and matrix inversion, respectively. We define the operator $\rm diag(\cdot)$ that returns the vector of the main diagonal of a given matrix, the operator $\rightarrow$, which denotes the deletion of a given element from a set and the operator $\#$, that returns the rank of a matriz, and the operator $\sim$ that sorts the elements of a vector in ascending order.

>>>>

\journal{Journal of Network and Computer Applications}

@@

In this paper, scalars are denoted by italic letters (\emph{a, b, A, B, $α$, $β$}), vectors by lowercase bold letters (\textbf{a, b}), matrices by uppercase bold letters (\textbf{A, B}), and $a_i,_j$ denotes the (\emph{i, j}) elements of the matrix \textbf{A}. The superscripts \textsuperscript{T} and \textsuperscript{-1} are used for matrix transposition and matrix inversion, respectively. We define the operator $\rm diag(\cdot)$ that returns the vector of the main diagonal of a given matrix, the operator $\uptarrow$, which denotes the deletion of a given element from a set and the operator $\#$, that returns the rank of a matriz, and the operator $\sim$ that sorts the elements of a vector in ascending order.
